### 2019-08-05 paper/paper.tex
Added original paper diagram
adding a paragraph and the paper current pdf file

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2019} with \usepackage[nohyperref]{icml2019} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

@@

CWE is a type of transfer learning method; a model is pretrained on a base dataset and fine tuned on the task dataset,  with the underlying hypothesis that information distilation is possible from one source (base dataset) to the other (task specific dataset).
The main reason for the great success of CWE is that the base model is trained using supervised learning on huge amounts of data, e.g. BERT, was trained on 3,300M words. the fact that CWE models are also self trained makes it easier to collect such huge amount of data without the need to label examples. the downside of this models is that they use many parameters (BERT Large - 330M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems. in the next section we will introduce the benchmark model which we aim to improve - BERT for CommonsenseQA (which is identical to BERT for SWAG) as was introduced in the original paper of BERT.

\subsection{BERT benchmark for SWAG}

\section{Methodology}

@@

Simply constructing a matrix with each cell being the score for the matching pair, normalizing each row so that we have a probability matrix, and then calculating the stationary distribution doesn't work well in practice. This is because normalizing the matrix causes the model to be unable to understand the absolute value of the scores, e.g. if it sees a row in which all values are similar, it can't differ the case in which all scores were low (and thus our "current" answer is good) from the case all of the scores were high.
Consider the following matrix:

>>>>

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2019} with \usepackage[nohyperref]{icml2019} above.
\usepackage{hyperref}
\usepackage{mathtools}
% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

@@

CWE is a type of transfer learning method; a model is pretrained on a base dataset and fine tuned on the task dataset,  with the underlying hypothesis that information distilation is possible from one source (base dataset) to the other (task specific dataset).
The main reason for the great success of CWE is that the base model is trained using supervised learning on huge amounts of data, e.g. BERT, was trained on 3.3B words. the fact that CWE models are also self trained makes it easier to collect such huge amount of data without the need to label examples. the downside of this models is that they use many parameters (BERT Large - 340M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems. in the next section we will introduce the benchmark model which we aim to improve - BERT for CommonsenseQA (which is identical to BERT for SWAG) as was introduced in the original paper of BERT.

\subsection{BERT}
BERT is a word based CWE model that was pre-trained on two learning objectives. given a sentence, predict masked words (15\% of the words were masked) and next sentence prediction. BERT’s  model  architecture is a multi-layer bidirectional Transformer encoder \cite{vaswani2017attention} with the following hyper-parameters (BERT Large) - 12 Transformer blocks, hidden size 1024 (H) and 16 self attention heads. BERT input can be one or two sentences.

BERT input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocab words. this way BERT stores only 30K vocabulary words very rarely encounter out-of-vocab words when tokenizing English texts. two special token are added for each sentence, a start token [CLS] and an end token [SEP]. if the input contains two sentences another [CLS] token is added in between the sentences. Due to the fact that Transformers do not encode the sequential nature of their inputs a segment ids and position embeddings are added as well to the input.

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{bert_input_repr}}
\caption{input representation for BERT (from the original paper).}
\label{bert_input_repr}
\end{center}
\vskip -0.2in
\end{figure}
fine tuning BERT is simply swapping out the appropriate input and output, whether the input is a single text or a text pair the input and output pairs are given to the model and the parameters are fine-tuned by back-propagation end to end after connecting to the [CLS] token embedding to a task specific classification layer with a given loss function.

\subsection{BERT baseline for SWAG}

In the BERT Paper, the authors approach the SWAG challange with the following input (input #\ref{original_input_order}). that input is fed to BERT architecture and the [CLS] token embedding is used to predict a logit by calculating a dot product with a learned vector. this process is done for each answer independently of each other and then a softmax layer with cross entropy loss is calculated to compute the error. As we can see, this architecture introduce only H (1024) new parameters to the existing BERT model.
\begin{equation}
[CLS][Question][SEP][Answer][SEP] 
\label{original_input_order}
\end{equation}

\section{CommonSeneseQA}
CommonSeneseQA is a dataset which specifically made for common sense reasoning, by asking crowd workers to generate questions from concepts from ConceptNet. it contains 12,247 examples and 5 answers per question. 
the Authors use the same architecture as in the BERT benchmark for SWAG
and report Accuracy score of 56.7\%. The current state of the art
on this dataset is currently 68.3\% accuracy, 23.6\% below human level.

\section{Methodology}
We propose a method with different variants to model the dependencies between answers, by feeding answer pairs jointly to BERT's architecture. by doing so, we contribute in different ways:

\begin{itemize}

\item making the model more expressive by removing the independence assumption

\item extending the model to deal with questions as 'what is largest?"

\item  extending the model to deal with answers as 'all answer are correct" or 'none of the above"

\end{itemize}

@@

Simply constructing a matrix with each cell being the score for the matching pair, normalizing each row so that we have a probability matrix, and then calculating the stationary distribution doesn't work well in practice. This is because normalizing the matrix causes the model to be unable to capture the absolute value of the scores, e.g. if it sees a row in which all values are similar, it can't differ the case in which all scores were low (and thus our "current" answer is good) from the case all of the scores were high.
Consider the following matrix:
